### 2022-07-14 manuscript.tex
Merge pull request #259 from SORTEE-Github-Hackathon/RCO-cover-letter-doi [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/956112ff108905503babe0eed04fa5ef9ddcd12b.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/956112ff108905503babe0eed04fa5ef9ddcd12b/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2673393113

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1871a551b58e817b71a630c86cdd3fb8268d2ada/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1871a551b58e817b71a630c86cdd3fb8268d2ada}{SORTEE-Github-Hackathon/manuscript@1871a55}
on July 14, 2022.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/956112ff108905503babe0eed04fa5ef9ddcd12b/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/956112ff108905503babe0eed04fa5ef9ddcd12b}{SORTEE-Github-Hackathon/manuscript@956112f}
on July 14, 2022.
